comgen-outline

### 2017-06-08 paper/generics-paper.Rmd
edits throughout model sections, adjust fig 1

We can make particular statements about objects, events, and causes.
We can say "My dog is friendly.", "John ran this afternoon.", or "My grandfather drank moonshine and it made him go blind."
To consider the corresponding generalizations (i.e., "Dogs are friendly", "John runs", "Drinking moonshines makes you go blind"), we must say exactly how the particular relates to the generalization.
We consider the generalization to be about a *category* and the particular to correspond to *instances* of that category.
Thus, *dog* is an instance of the category \textsc{dogs}, *John at a particular time* is an instance of the category of \textsc{john}, and *drinking moonshine at a particular time* is an instance of the category of \textsc{drinking moonshine} (see Table \ref{tabgenPart}).

Suppose we observe instances $\{x_1, x_2, ..., x_n\}$ of category $k$ and some number of them have feature $f$: What do we learn about possible future instances of $x_{n+1}$, particularly with respect to $f$?
For properties among instances of a category, we can describe an inductive inference by a probability $h$ $h = P(x \in f \mid x \in k)$^[
With a frequentist interpretation, this can be thought of as the *prevalence* of $f$ among $k$.
].
In the study of categories and properties, $x$ is an object.
For a behavior exhibited by an agent, the inference concerns a rate --- how frequently (in time) does $x \in f$ occur --- which can be described as a probability integral: $h = \int_{t} P(x \in f_t \mid x \in k_t) \diff t$
In this case, $x$ is a instance of an agent.
Causal learning can be described with the same formalism as for categories, a probability referring to the probability of an effect $e$ given a cause $c$: $h = P(x \in e \mid x \in c)$.
We refer to this probability as $h$ because it represents a hypothesis about the underlying causal power or frequency that generated the observed data.
<!-- A Bayesian agent will have prior beliefs about the probability (potentially an uninformed prior) and uses Bayesian inference to learn about the probability from her observations. -->

@@

The human capacity to generalize from observations has been studied extensively in cognitive and developmental psychology [@Nisbett1983; @Baldwin1993; @Heit2000].
Inductive inferences show complex sensitivites to the kind of observations, and even how those observations came to be observed in the first place.
For instance, observing that an indigenous person living on a remote island *is obese* provides considerably less information about the weights of other islanders in comparison to inferences about skin color upon learning that one islander's skin color *is brown* [@Nisbett1983].
Confounded causal evidence can be suddenly become unconfounded when you know the evidence was generated by an intentional agent [@Goodman2009].
Quantitative modeling has been crucial in explaining how the subtleties of experience relate to subtleties in generalization [@Tenenbaum2006; @Kemp2008].

Studying generalizations from observational evidence can only take us so far in understanding how the mind understands the world or culture accumulates across generations.
Relying upon observations would be particularly problematic to learn, for example, about properties that are difficult to observe (e.g., *cows have four stomachs*) or events that are statistically unlikely (e.g., *lightning strikes tall objects*).
For abstract, generalizable knowledge to remain in a culture, it must be able to be faithfully transmitted between individuals and across generations [@Tomasello1999], and language provides simple ways to communicate generalizations.

@@

We will discuss communicating generalizations in the context of generalizations about categories (i.e., *generic language*), though the arguments will extend to events and causes as well, following the formalization described in the previous section. 
Generics express a relation between a kind K (e.g., \textsc{dogs}) and a property F (e.g., \textsc{is friendly}), such that the property can also be said to be applicable of an individual (i.e., "My dog is friendly"). 
Bare plural statements (e.g., *Dogs are friendly*) strongly tend to yield a generic meaning, though other forms can express such a meaning [e.g., *A mongoose eats snakes.*; @Carlson1977] .

Given that generics express a property that can be applied to individuals, it seems intuitive that what makes the statement true or false would correspond to the number of individuals who hold the property.
At first glance, generics convey that *most* have the property, such as *Most dogs are friendly*.
*Robins lay eggs* is true, though, despite the fact that only female robins lay eggs (not exactly *most robins*). 
If generic statements can be true by restricting themselves to only be describing females, why does *Robins are female* seem like a weird statement to make?
Finally, *Mosquitos carry malaria* is intuitively true despite malaria only being present in a tiny fraction of a percentage of mosquitos.
It seems that any hard condition on the prevalence of the feature in the category (e.g., how many robins lay eggs) would violate intuitions.

@@

The *generics as default* view capitalizes on general cognitive principles to explain why certain generics are true or not.
*Mosquitos carry malaria* conveys a dangerous or striking property, which is useful to know about if you are trying to survive in a dangerous world.
This theory thus predicted that generics that convey striking properties would be true even if they were relatively rare (e.g., *Sharks attack swimmers*), which has been empirically verified [@Cimpian2010; @Prasada2013].
Other generics convey properties that are *characteristic* of a kind, such as *Robins lay eggs*, argued to have a *principled connection* between kind and property [@Prasada2006; @Prasada2013].

Yet, generics are not limited to conveying rich relations. 
Arbitrary relations can also be expressed like *Barns are red* or *Ravens are bigger than toasters*, which seem only to be true because of the statistics of the world [@Nickel2008; @Nickel2016; @Sterken2015].
The *generics as default* view must then be supplemented with the principle that, in certain situations, the statistics can influence generic endorsement.
How do we make sense of this panoply of conditions?
Is there some more general, unified principle that explains what makes generic statements true or false?

Bayesian cognitive models are used to represent flexible, structured knowledge of the world and formalize the inferences that people draw using such conceptual representations [e.g., @Kemp2008; @Goodman2015Chapter].
The basic currency of inference in these models is probability.
In the case of generic language, we posit that conceptual factors may influence the meaning of a generic statement via its influence on subjective probability.
If that's true, a simple, semantic theory (e.g., a threshold on subjective probability) may be enough to formalize the core meaning of a generic statement.

\begin{eqnarray}
L(h \mid u) &\propto& {\delta_{\denote{u}(h, \theta)} \cdot P(h)} \label{eq:L0fixed}
\end{eqnarray}

Equation \ref{eq:L0fixed} is a model of a listener $L$ who updates her beliefs $h$ according the meaning an utterance $u$.
$P(h)$ represents the listener's prior world knowledge concerning the relevant probabilities $h$.
The particular form of the prior plausibly depends upon the kind of property or event in question and could be structured as a result of deeper conceptual knowledge about properties and events [cf., @Griffiths2005; @Tenenbaum2006; @Kemp2008].
We term this prior distribution the *prevalence prior*.
$\delta_{\denote{u}(h, \theta)}$ is the likelihood term in Bayes' Rule, representing the literal semantics of utterances.
For an utterance conveying a generalization $u_{gen}$, we adopt a simple threshold semantics:

@@

The $\delta_{\denote{u}(h, \theta)}$ likelihood is the Kronecker delta function returning $1$ for states $h$ greater than threshold $\theta$ and $0$ otherwise. 
Logical quantifiers can be described using threshold semantics (i.e., *some* is $h > 0$, all is $h = 1$).
What threshold $\theta$ should be used for the generic generalization?
We posit that meaning of a generalization in language is *underspecified*; that is, there is not a fixed $\theta$ that corresponds to the generalization, but rather the listener must infer $\theta$ in context.
In the probabilistic model, this is formalized as a prior distribution over the value of $\theta$.
We assume this prior is uninformed: $\theta \sim \text{Uniform}(0, 1)$.

@@

This is a Bayesian model of interpreting a statement conveying a generalization whose meaning is simple (i.e., a threshold function) but underspecified.
Figure \ref{fig:simulations} shows model $L$'s posterior distribution on $h$ upon hearing utterances corresponding to the uncertain threhsold (Eq. \ref{eq:L0}) as well as a comparison model using a fixed threshold at 0 (intuitively, corresponding to the quantifier "some").
The differences in the semantics are easily seen when considering a uniform distribution over $h$ (top left facet).
"Some" rules out only the lowest possible state and returns a posterior very similar to the prior.
The behavior of the generalization is distinct: The higher the $h$, the more likely the state is.

The intuition behind this behavior can be gleaned by imagining what the $L$ listener would believe with different thresholds and averaging over those possibilities.
If the threshold is very high, only the highest $h$ would pass the threshold.
If the threshold is slightly lower but still high, the highest $h$ probabilities would still pass the threshold, as would some that are slightly lower.
As the threshold takes on lower and lower values, more and more probabilities would surpass it.
When the threshold is very low, almost all probabilities are consistent with it (akin to "Some").
When the listener averages over these thresholds, higher values of $h$ pass more thresholds; thus, higher $h$ are more likely *a posteriori*.

@@

In RSA, language production and comprehension are defined by recursive Bayesian models describing speaker and listener.
Following RSA, this speaker is assumed to be an approximately rational Bayesian agent with degree with rationality governed by parameter $\lambda$.
The speaker's decision to say an utterance (e.g., the generalization) is determined with respect to how well it would communicate $h$ to the listener $L$, in comparison to alternative utterances.
To model generic endorsement, this decision is evaluated in comparison to the alternative of *not saying the generalization*;
with just two alternatives (say the generalization vs. not), the model can be interpreted as a model of felicity judgments [@Degen2014]. 
Formally, we consider the negative alternative as the option of staying quiet, which carries no information content^[
This alternative can be realized in at least two other ways: the speaker could have said the negation of the utterance (i.e., *The generalization is not true.*) or the negative generalization (i.e., *The opposite is true.*, e.g., *Ks do not have F*).
All results reported are similar for these two alternatives, and we use the alternative of the *silent* utterance for simplicity.
]:

@@

@@

```{r simulations, fig.width = 8, fig.height=5}
all.simulations %>%
  mutate(Distribution = paste(Distribution, utterance, sep = "_")) %>%
  filter(Distribution != "Some", Distribution != "Most", Distribution != "Prior_generic") %>%
  mutate(Distribution = factor(Distribution, levels = 
                             c("Prior_some", "Posterior_Generalization_some", "Posterior_Generalization_generic"),
                                labels = c("Prior/Silence", "Some", "Generalization")),
         PriorShape = fct_relevel(PriorShape, "uniform", "barks","laysEggs","carriesMalaria","isFemale"
                                  #"eatsFood","areSick", "uniformRare", 
                                  #"carriesMalaria"
                                  )
         ) %>%
  ggplot(., aes(x = value, #y = prob, 
                #lty = Distribution, 
                color = Distribution, fill = Distribution))+
    geom_density(#stat= 'identity', 
                aes(y = ..scaled..),
                 size = 0.6, alpha = 0.7, adjust = 1.5)+
    #geom_bar(stat = 'identity', position = position_dodge(), color = 'black')+
    theme_few() +
    #scale_color_solarized()+
    #scale_fill_solarized()+
    #scale_fill_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
    #scale_color_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
   scale_fill_manual(values = c("#636363", "#2b83ba","#d7191c"))+
    scale_color_manual(values = c("#636363","#2b83ba", "#d7191c"))+
    #scale_linetype_manual(values = c(3, 4, 2, 1))+
    scale_linetype_manual(values = c(3, 4, 1))+
    scale_x_continuous(breaks = c(0, 0.5, 1), limits= c(0, 1))+
    xlab("Degree of propensity (probability)") +
    ylab("Probability density") +
  facet_grid(PriorShape~Distribution, scales = 'free')+
  theme(strip.text.y = element_text(angle = 0))
```

@@

All of the RSA models defined in the previous section predict that the interpretation and endorsement of a generalization depends listener's *a priori* beliefs about the probabilty in question $P(h)$.
Qualitatively, the predictions of the different formulations of the RSA models for understanding generalizations are not appreciably different (though their quantitative predictive flexibility is).
For purposes of illustration, we present present predictions of the simplest model with an underspecified threshold and a model where the threshold is fixed to 0 (corresponding intuitively to *some* statements).

Before, we described how an underspecified threshold interacts with a uniformly uncertain belief about the probability.
Here, we consider some canonical cases from the literature on generics to demonstrate the kind of inferences a listener would draw from different generic statements.
Our model of endorsements is a model of speaker who decides whether or not to say the generic or stay silent. 
Thus, qualitatively model predictions for endorsement can be gleaned by comparing the prior distribution over the probability $h$ (which is the same as posterior upon hearing "silence") with the posterior distribution over $h$ upon hearing the generalization.

In Figure \ref{fig:simulations} (row 2), we show a schematic prior distribution over a feature "barks".
Here, we show the prior is bimodal with peaks at 0\% and some high prevalence values, corresponding intuitively to the fact that many kinds creatures do not bark (i.e., have 0\% prevalence) and for those that do have members that bark, many of them bark (i.e., have some high prevalence value).
The fact that "those that do not bark" is not just a Delta function at 0\% reflects the intuitive possibility that some members of a kind who does not usually bark (say, a cat) could somehow have the feature (e.g., due to some transient or accidental state).
We see that the quantifier "Some" (middle row) struggles to differentiate those that accidentally do have the feature from those that usually have the feature, returning a posterior distribution very similar to the prior.
Hearing the generalization ("Dogs bark"), however, strongly signals the property is widespread in the category.

The strength of a listener's inference (i.e., how prevalent is the feature?) depends in systematic ways on the prior belief distribution over the prevalence of the feature.
Consider a prior intuitively corresponding to the feature "lays eggs" (Figure \ref{fig:simulations}, row 3). 
The listener's posterior upon hearing the generalization (e.g., "Robins lay eggs") is much more conservative than with "barks" prior: The listener thinks that about 50% of robins lay eggs.
Indeed, this is the same inference as if a listener heard "Robins are female" (Figure \ref{fig:simulations}, row 4, right panel). 
The intuitive differences in the endorsements of these statements comes from the speaker's comparison to what a listener would believe if she stayed silent (i.e., the listener's prior).
In the case of "are female", the posterior is nearly identical with the prior; thus, the utterance has very litle information content.

@@

In the rest of this paper, we examine the validity and generality of this theory of communicating generalizations through three case studies: generalizations about categories, events, and causes.

>>>>

Particular statements can be made about objects, events, and causes.
We can say "My dog is friendly.", "John ran this afternoon.", or "My grandfather drank moonshine and it made him go blind."
To consider the corresponding generalizations (i.e., "Dogs are friendly", "John runs", "Drinking moonshines makes you go blind"), we must specify exactly how the particular relates to the generalization.
We consider the generalization to be about a *category* and the particular to correspond to *instances* of that category.
Thus, *dog* is an instance of the category \textsc{dogs}, *John at a particular time* is an instance of the category of \textsc{john}, and *drinking moonshine at a particular time* is an instance of the category of \textsc{drinking moonshine} (see Table \ref{tabgenPart}).

Suppose we observe instances $\{x_1, x_2, ..., x_n\}$ of category $k$ and some number of them have feature $f$: What do we learn about possible future instances of $x_{n+1}$, particularly with respect to $f$?
For properties among instances of a category, we can describe an inductive inference by a probability $h$ $h = P(x \in f \mid x \in k)$^[
With a frequentist interpretation, this can be thought of as the *prevalence* of $f$ among $k$.
].
<!-- In the study of categories and properties, $x$ is an object. -->
For an action exhibited by an agent, the inference concerns a rate --- how frequently (in time) does $x \in f$ occur --- which can be described as a probability integral: $h = \int_{t} P(x \in f_t \mid x \in k_t) \diff t$
<!-- In this case, $x$ is a instance of an agent. -->
Causal learning can be described with the same formalism as for categories, a probability referring to the probability of an effect $e$ given a cause $c$, known as causal power: $h = P(x \in e \mid x \in c)$.
Throughout, we refer to the degree of probability as $h$ because it represents a hypothesis about the underlying causal power or frequency that generated the observed data.
<!-- A Bayesian agent will have prior beliefs about the probability (potentially an uninformed prior) and uses Bayesian inference to learn about the probability from her observations. -->

@@

The human capacity to generalize from observations has been studied extensively in cognitive and developmental psychology [@Nisbett1983; @Baldwin1993; @Heit2000].
Inductive inferences show complex sensitivites to the kind of observations, and even how those observations came to be observed in the first place.
For instance, observing that an indigenous person living on a remote island *is obese* provides considerably less information about the weights of other islanders in comparison to inferences about skin color upon learning that one islander's skin color *is brown* [@Nisbett1983].
This subtlety can be modeled using heirarchical models to elaborate the prior in a Bayesian model [@Kemp2008].
Confounded causal evidence can be suddenly become unconfounded when you know the evidence was generated by an intentional agent, which is predicted assuming the data-generating process (i.e., the likelihood function) is another agent [@Goodman2009].

Studying generalizations from observational evidence can only take us so far, however, in understanding how the mind understands the world or culture accumulates across generations.
Relying upon observations would be particularly problematic to learn, for example, about properties that are difficult to observe (e.g., *cows have four stomachs*) or events that are statistically unlikely (e.g., *lightning strikes tall objects*).
For abstract, generalizable knowledge to remain in a culture, it must be able to be faithfully transmitted between individuals and across generations [@Tomasello1999], and language provides simple ways to communicate generalizations.

@@

We will discuss communicating generalizations in the context of generalizations about categories (i.e., *generic language*), though the arguments will extend to events and causes as well, following the definitions of $h$ described in the previous section. 
Generics express a relation between a kind K (e.g., \textsc{dogs}) and a property F (e.g., \textsc{is friendly}), such that the property can also be said to be applicable of an individual (i.e., "My dog is friendly"). 
Bare plural statements (e.g., *Dogs are friendly*) strongly tend to yield a generic meaning, though other forms can express such a meaning [e.g., *A mongoose eats snakes.*; @Carlson1977] .

Given that generics express a property that can be applied to individuals, it seems intuitive that what makes the statement true or false would correspond to the number of individuals who hold the property.
At first glance, generics convey that *most* have the property, such as *Most dogs are friendly*.
*Robins lay eggs* is true, though, despite the fact that only female robins lay eggs, which is debatable whether or not that counts as *most robins*. 
If generic statements can be true by restricting themselves to only be describing females, why does *Robins are female* seem like a weird statement to make?
Finally, *Mosquitos carry malaria* is intuitively true despite malaria only being present in a tiny fraction of a percentage of mosquitos.
It seems that any hard condition on the prevalence of the feature in the category (e.g., how many robins lay eggs) would violate intuitions.

@@

The *generics as default* view capitalizes on general cognitive principles to explain why certain generics are true or not.
*Mosquitos carry malaria* conveys a dangerous or striking property, which is useful to know about if you are trying to survive in a hostile world.
This theory thus predicted that generics that convey striking properties would be true even if they were relatively rare (e.g., *Sharks attack swimmers*), which was empirically corroborated [@Cimpian2010; @Prasada2013].
Other generics convey properties that are *characteristic* of a kind, such as *Robins lay eggs*, argued to have a *principled connection* between kind and property [@Prasada2006; @Prasada2013].

Yet, generics are not limited to conveying rich relations. 
Arbitrary relations can also be expressed such as *Barns are red* or *Ravens are bigger than toasters*, which seem only to be true because those are the statistics of the world [@Nickel2008; @Nickel2016; @Sterken2015].
The *generics as default* view must then be supplemented with the principle that, in certain situations,  statistics can influence generic endorsement.
How do we make sense of this panoply of conditions?
Is there some more general, unified principle that explains what makes generic statements true or false?

Bayesian cognitive models are used to represent flexible, structured knowledge of the world and formalize the inferences that people draw using such conceptual representations [e.g., @Kemp2008; @Goodman2015Chapter].
The basic currency of inference in these models is probability.
In the case of generic language, we posit that conceptual factors may influence the meaning of a generic statement via its influence on subjective probability.
If that's true, a simple, semantic theory (e.g., a threshold on subjective probability) may be enough to formalize the core meaning of a generic statement $u_{gen}$:

@@

$\delta_{\denote{u}(h, \theta)}$ is the Kronecker delta function returning $1$ for states $h$ greater than threshold $\theta$ and $0$ otherwise. 
Logical quantifiers can be described using threshold semantics (i.e., *some* is $h > 0$, all is $h = 1$).
What threshold $\theta$ should be used for the generic generalization?
We posit that meaning of a generalization in language is *underspecified*; that is, there is not a fixed $\theta$ that corresponds to the generalization, but rather the listener must infer $\theta$ in context.
In the probabilistic model, this is formalized as a prior distribution over the value of $\theta$.
We assume this prior is uninformed: $P(\theta) = \text{Uniform}(0, 1)$.

@@

Equation \ref{eq:L0} is a model of a listener $L$ who updates her beliefs $h$ according the meaning an utterance $u$.
$P(h)$ represents the listener's prior world knowledge concerning the relevant probabilities $h$.
The particular form of the prior plausibly depends upon the kind of property or event in question and could be structured as a result of deeper conceptual knowledge about properties and events [cf., @Griffiths2005; @Tenenbaum2006; @Kemp2008].
We term this prior distribution the *prevalence prior*.
$\delta_{\denote{u}(h, \theta)}$ is the likelihood term in Bayes' Rule, representing the literal semantics of utterances.

<!-- \begin{eqnarray} -->
<!-- L(h \mid u) &\propto& {\delta_{\denote{u}(h, \theta)} \cdot P(h)} \label{eq:L0fixed} -->
<!-- \end{eqnarray} -->

This is a Bayesian model of interpreting a statement conveying a generalization whose meaning is simple (i.e., a threshold function) but underspecified.
Figure \ref{fig:simulations} shows model $L$'s posterior distribution on $h$ upon hearing utterances corresponding to the uncertain threhsold (Eq. \ref{eq:L0}) as well as a comparison model using a fixed threshold at 0 (intuitively, corresponding to the quantifier "some").
The differences in the semantics are easily seen when considering a uniform distribution over $h$ (top left facet).
The fixed threshold model rules out only the lowest possible state and returns a posterior very similar to the prior.
The behavior of the generalization is distinct: The higher the $h$, the more likely the state is.

The intuition behind this behavior can be gleaned by imagining what the $L$ listener would believe with different thresholds and averaging over those possibilities.
If the threshold $\theta$ is very high, only the highest $h$ would pass the threshold.
If the threshold $\theta$  is slightly lower but still high, the highest $h$ probabilities would still pass the threshold, as would some that are slightly lower.
As the threshold $\theta$  takes on lower and lower values, more and more $h$ probabilities would surpass it.
When $\theta$ is very low, almost all $h$ are consistent with it (akin to "Some").
When the listener averages over these thresholds, higher values of $h$ pass more thresholds; thus, higher $h$ are more likely *a posteriori*.

@@

In RSA, language production and comprehension are defined by recursive Bayesian models describing speaker and listener.
Following RSA, this speaker is assumed to be an approximately rational Bayesian agent with degree with rationality governed by parameter $\lambda$.
The speaker's decision to say an utterance (e.g., the generalization) is determined with respect to how well it would communicate $h$ to the listener $L$, in comparison to alternative utterances.
To model endorsement, this decision is evaluated in comparison to the alternative of *not saying the generalization*;
with just two alternatives (say the generalization vs. not), the model can be interpreted as a model of felicity judgments [@Degen2014]. 
Formally, we consider the negative alternative as the option of staying quiet, which carries no information content^[
This alternative can be realized in at least two other ways: the speaker could have said the negation of the utterance (i.e., *The generalization is not true.*) or the negative generalization (i.e., *The opposite is true.*, e.g., *Ks do not have F*).
All results reported are similar for these two alternatives, and we use the alternative of the *silent* utterance for simplicity.
]:

@@

The pair of speaker-listener models presented above correspond to the simplest possible communicative models with an underspecified threshold-meaning for a generalization. 
This *simple but underspecified* hypothesis defines a class of models with potentially more levels of recursion (e.g., a listener who thinks about a speaker who thinks about a listener).
We discuss these alternative formulations (all of which are instances of the *simple but underspecified* hypothesis) and provide formal model comparisons between these RSA models in Appendix A.

@@

```{r simulations, fig.width = 8, fig.height=5}
all.simulations %>%
  mutate(Distribution = paste(Distribution, utterance, sep = "_")) %>%
  filter(Distribution != "Some", Distribution != "Most", Distribution != "Prior_generic") %>%
  mutate(Distribution = factor(Distribution, levels = 
                             c("Prior_some",  "Posterior_Generalization_generic", "Posterior_Generalization_some"),
                                labels = c("Prior/Silence",  "Generalization (Uncertain threshold)", "Fixed threshold")),
         PriorShape = factor(PriorShape, levels = c("uniform", "barks","laysEggs","carriesMalaria","isFemale"),
                             labels = c("uniform", "bark","lay eggs","carry malaria","are female")
                                  #"eatsFood","areSick", "uniformRare", 
                                  #"carriesMalaria"
                                  )
         ) %>%
  ggplot(., aes(x = value, #y = prob, 
                #lty = Distribution, 
                color = Distribution, fill = Distribution))+
    geom_density(#stat= 'identity', 
                aes(y = ..scaled..),
                 size = 0.6, alpha = 0.7, adjust = 1.5)+
    #geom_bar(stat = 'identity', position = position_dodge(), color = 'black')+
    theme_few() +
    #scale_color_solarized()+
    #scale_fill_solarized()+
    #scale_fill_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
    #scale_color_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
   scale_fill_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
    scale_color_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
    #scale_linetype_manual(values = c(3, 4, 2, 1))+
    scale_linetype_manual(values = c(3, 4, 1))+
    scale_x_continuous(breaks = c(0, 0.5, 1), limits= c(0, 1))+
    scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
    xlab("Degree of probability h") +
    ylab("Scaled probability density") +
  facet_grid(PriorShape~Distribution, scales = 'free')+
  guides(fill = F, color = F)+
  theme(strip.text.y = element_text(angle = 0))
```

@@

The RSA model defined in the previous section predicts that the endorsement of a generalization depends upon a listener's *a priori* beliefs about the probabilty in question $P(h)$.
For purposes of illustration, we present present the listener $L$ interpretations of the generalization for the underspecified threshol model as well as a fixed threshold model where the threhsold is set to the lowest possible value, corresponding intuitively to the quantifier *some* (Figure \ref{fig:simulations}).

Above, we described the intuition for how an underspecified threshold interacts with a uniformly uncertain belief about the probability $h$.
Here, we consider some canonical cases from the literature on generics to demonstrate the kind of inferences a listener would draw from different generic statements.
Note that our model of endorsements is a model of a speaker who decides whether or not to say the generic or stay silent. 
Qualitatively speaking, model predictions for endorsement can be gleaned by comparing the posterior distribution over the probability $h$ upon hearing the generalization with the prior distribution over $h$ (which is the same as the listener's posterior upon hearing "silence").
For different degrees of target probability $h$ that the speaker wants to communicate, the generalization will be more or less good at communicating it.

In Figure \ref{fig:simulations} (row 2), we show a schematic prior distribution over a feature "barks".
Here, we posit the prior is bimodal with peaks near 0\% and some high prevalence values, corresponding intuitively to the fact that many kinds creatures do not bark (i.e., have $h \sim 0$) and for those that do have members that bark, many of them bark (i.e., have some high $h$).
<!--  -->
We see that the fixed threshold (middle row) struggles to differentiate those that generally do not have the feature from those that usually have the feature, returning a posterior distribution very similar to the prior.^[
We model "those that do not generally have the feature" a Beta distribution with an expected value (mean) close to zero. 
The fact that this component of the prior is not just a Delta function at 0\% reflects the intuitive possibility that some members of a kind who do not generally have the feature (e.g., a cat who barks) could somehow acquire the feature from accidental or transient causes (e.g., a strange genetic mutation).
]
Hearing the generalization ("Dogs bark"), however, strongly signals the property is widespread in the category.

The strength of a listener's inference about $h$ (i.e., how prevalent is the feature?) depends in systematic ways on the prior belief distribution over $h$.
Consider a prior intuitively corresponding to the feature "lays eggs" (Figure \ref{fig:simulations}, row 3). 
The listener's posterior upon hearing the generalization (e.g., "Robins lay eggs") is much more conservative than with "barks" prior: The listener thinks that about 50% of robins lay eggs.
Indeed, this is the same inference as if a listener heard "Robins are female" (Figure \ref{fig:simulations}, row 4, right panel). 
Differences in the endorsements of these two statements would come from the speaker's comparison to what a listener would believe if she stayed silent (i.e., the listener's prior).
In the case of "are female", the posterior is nearly identical with the prior; thus, the utterance has very litle information content.

@@

In sum, these simulations show that the behavior of the uncertain-threshold semantics is distinct from both the prior distribution over probability $h$ as well as the inferences derived from a fixed-threshold semantics.
In the rest of this paper, we examine the behavior of the speaker model as a model of endorsements through three case studies: generalizations about categories, events, and causes.
